Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-09-28 manuscript/main.tex
Plot updates (ncsl, ideology)
- Ideology plot in greyscale
- Added ideology plot with alignments on log scale
- Added ncsl cosine similarity plot
- Updated ncsl caption with linetypes

\usepackage{graphicx} 
%\usepackage{subfig} 
\usepackage{pdflscape} 
\usepackage{booktabs} 
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{color}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{xr}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{amsfonts}
\usepackage{subfigure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/ncsl_pr_nosplit.png}
\caption{Precision-Recall curve for classifying two bills being in the same
    ncsl table by thresholding the bill-dyad alignment score. The x axis
displays the threshold, the y axis represents precision and recall. The shaded
area in the background displays the frequency distribution of the alignment
scores.}
\label{fig:ncsl_prec_rec}
\end{figure}

%\begin{figure}[t!]
%    \centering
%    \begin{subfigure}[b]{0.5\textwidth}
%        \centering
%        \includegraphics[height=1.2in]{figures/ncsl_pr_nosplit.png}
%        \caption{Lorem ipsum}
%    \end{subfigure}%
%    ~ 
%    \begin{subfigure}[b]{0.5\textwidth}
%        \centering
%        \includegraphics[height=1.2in]{figures/ncsl_pr_cosim.png}
%        \caption{Lorem ipsum, lorem ipsum,Lorem ipsum, lorem ipsum,Lorem ipsum}
%    \end{subfigure}
%    \caption{Caption place holder}
%\end{figure}

@@

In order to investigate this pattern more closely, we additionally calculate
quantile regressions for the relationship between the alignment score and the
ideological distance. In a quantile regression, the dependent variable is the value of the predicted quantile of the distribution of the dependent variable conditional on the independent variables (e.g., the predicted median for median regression with the quantile set to 0.50 \citep{harden2011linear}). Figure \ref{fig:quantile_regression} displays the
coefficients from quantile regressions on a sequence of quantiles from the
median to the 0.995th quantile. Confidence intervals are calculated by resampling bills, which represents an implementation of the clustered nonparametric bootstrap \citet[see e.g.][]{harden2011bootstrap}. Coefficients significant at the 95\% level are displayed in black, insignificant coefficients are grey. We see that there is only a very weak relationship between the ideological similarity of bill sponsors and the median alignment scores between bills. However, as the quantile we model increases we see that the relationship grows strong and negative in magnitude, and is statistically significant. These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse as a measure of policy similarity.

\begin{figure}[ht!]i
    \centering
    \includegraphics[width=0.8\textwidth]{figures/ideology_plot.png}
    \caption{Hexbin plot of alignment score and ideological distance of all 50 million bill dyads.}
    \label{fig:ideology_plot}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/quantile_regression.png}
    \caption{Coefficients of quantile regression for alignment score on
    ideological distance. Dots indicate the point estimate. Horizontal bar
represent 95\% confidence intervals obtained via the clustered bootstrap, [using
1200 iterations]. Note that the x-axis is not in a natural scale}
    \label{fig:quantile_regression}
\end{figure}

>>>>

\usepackage{graphicx} 
%\usepackage{subfig} 
\usepackage{pdflscape} 
\usepackage{booktabs} 
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{color}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{xr}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{amsfonts}
%\usepackage{subfigure}
\usepackage{subcaption}

@@

%\begin{figure}
%\centering
%\includegraphics[width=0.8\textwidth]{figures/ncsl_pr_nosplit.png}
%\caption{Precision-Recall curve for classifying two bills being in the same
%    ncsl table by thresholding the bill-dyad alignment score. The x axis
%displays the threshold, the y axis represents precision and recall. The shaded
%area in the background displays the frequency distribution of the alignment
%scores.}
%\label{fig:ncsl_prec_rec}
%\end{figure}

\begin{figure}[ht!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ncsl_pr_nosplit.png}
        \caption{Precision-Recall curve for classifier based on alignment scores.}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ncsl_pr_cosm.png}
        \caption{Precision-Recall curve for classifier based on cosine similarity.}
    \end{subfigure}
    \caption{Precision-Recall curve for classifying two bills being in the same
    ncsl table by thresholding the bill-dyad alignment score. The dotted (yellow) line is recall, the solid (black) line is precision. The x axis
displays the threshold, the y axis represents precision and recall. The shaded
area in the background displays the frequency distribution of the alignment
scores.}
\label{fig:ncsl_prec_rec}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ideology_plot.png}
        \caption{Hexbin plot with alignments on natural scale.}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ideology_plot_log.png}
        \caption{Hexbin plot with alignments on $log_{10}$ scale.}
    \end{subfigure}
    \caption{Hexbin plot of alignment score and ideological distance of all 50
    million bill-dyads. The shading of the bins indicates the density of data in
    the bin.}
    \label{fig:ideology_plot}
\end{figure}

In order to investigate this pattern more closely, we additionally calculate
quantile regressions for the relationship between the alignment score and the
ideological distance. In a quantile regression, the dependent variable is the value of the predicted quantile of the distribution of the dependent variable conditional on the independent variables (e.g., the predicted median for median regression with the quantile set to 0.50 \citep{harden2011linear}). Figure \ref{fig:quantile_regression} displays the
coefficients from quantile regressions on a sequence of quantiles from the
median to the 0.995th quantile. Confidence intervals are calculated by
resampling bills, which represents an implementation of the clustered
nonparametric bootstrap \citep{harden2011bootstrap}. Coefficients significant at the 95\% level are displayed in black, insignificant coefficients are grey. We see that there is only a very weak relationship between the ideological similarity of bill sponsors and the median alignment scores between bills. However, as the quantile we model increases we see that the relationship grows strong and negative in magnitude, and is statistically significant. These results both validate the use of text reuse as a measure of policy similarity, and reinforce the high precision and low recall nature of text reuse as a measure of policy similarity.

%\begin{figure}[ht!]i
%    \centering
%    \includegraphics[width=0.8\textwidth]{figures/ideology_plot.png}
%    \caption{Hexbin plot of alignment score and ideological distance of all 50
%    million bill dyads. The shading of the bins indicates the density of data in
%the bin.}
%    \label{fig:ideology_plot}
%\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/quantile_regression.png}
    \caption{Coefficients of quantile regression for alignment score on
    ideological distance. Dots indicate the point estimate. Horizontal bar
represent 95\% confidence intervals obtained with clustered bootstrap. 
Note that the x-axis is not in a natural scale.}
    \label{fig:quantile_regression}
\end{figure}
